Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-10-05 paper/manuscript.tex
Remove deprecated software

In general, there are many ways to calculate an MCSS. One of the most prominent approaches is to estimate the MCSS with a 2D subgraph isomorphism solver(SIS) using the 2D topological stuructre information of molecules\cite{raymond2002maximum}.
A large number of software tools can compute SIS MCSS matches using different cheminformatics packages. Some rely on RDKit~\cite{rdkit2019Dec}, such as pmx~\cite{gapsys2015pmx}, LOMAP~\cite{liu2013lead}, FESetup~\cite{loeffler2015fesetup}, ProtoCaller~\cite{suruzhon2020protocaller}, SMArt~\cite{petrov2021perturbation}, and partially BioSimSpace~\cite{hedges2019biosimspace}, while others such as fkcombu~\cite{kawabata20143d} are standalone tools. Schr\"{o}dinger's FEP+ planning tool was originally based on a version of LOMAP, and it also uses MCSS matching as well as 3D considerations to plan the network of single topology calculations between molecules~\cite{wang2015accurate}.

@@

	\item \href{https://github.com/protocaller/ProtoCaller}{ProtoCaller}, a setup tool for the automation of Gromacs free energy calculations~\cite{suruzhon2020protocaller}.
	\item \href{https://fesetup.readthedocs.io/en/latest/introduction.html}{FESetup} has been developed primarily to setup calculations in AMBER, GROMACS and SIRE~\cite{loeffler2015fesetup}.

@@

	\item Alchemlyb: Multipackage free energy analysis
	\url{https://github.com/alchemistry/alchemlyb}~\cite{daviddotson2020alchemistry}.
	\item pymbar: MBAR implementation, but have to roll your own analysis wrapper      
	\url{https://github.com/choderalab/pymbar} \cite{shirts2008statisticallya}.
	\item \href{https://github.com/OpenFreeEnergy/cinnabar}{Cinnabar}: Standardising alchemical free energy analysis. Includes tools for calculating network-wide analyses and deriving absolute free energies using a maximum-likelihood estimator \cite{richard_gowers_2025_15678719}.
	\item Free Energy Workflows: Sire-specific free energy map analysis using weighted path averages 
        \item \href{https://gitlab.com/RutgersLBSR/fe-toolkit}{FE-Toolkit}: collection of packages for free energy analysis, including network-wide MBAR analysis~\cite{giese2025fe}.
    \url{https://github.com/michellab/freenrgworkflows}.
    \item \href{http://www.ties-service.org}{TIES}: Perform statistical analysis of the output of alchemical ensemble simulations and report reliable predictions along with statistical uncertainties for a variety of free energy estimators \url{https://github.com/UCL-CCS/TIES_MD} \cite{bieniek2023}.
	\end{itemize}
\item[] Generally, commercial software will offer more complete pipelines in which standalone analysis applications are not necessarily needed; free and open source packages often require manual analysis but allow more flexibility and modification.
\end{itemize}

>>>>

In general, there are many ways to calculate an MCSS. One of the most prominent approaches is to estimate the MCSS with a 2D subgraph isomorphism solver(SIS) using the 2D topological stuructre information of molecules\cite{raymond2002maximum}.
A large number of software tools can compute SIS MCSS matches using different cheminformatics packages. Some rely on RDKit~\cite{rdkit2019Dec}, such as pmx~\cite{gapsys2015pmx}, LOMAP~\cite{liu2013lead}, SMArt~\cite{petrov2021perturbation}, and partially BioSimSpace~\cite{hedges2019biosimspace}, while others such as fkcombu~\cite{kawabata20143d} are standalone tools. Schr\"{o}dinger's FEP+ planning tool was originally based on a version of LOMAP, and it also uses MCSS matching as well as 3D considerations to plan the network of single topology calculations between molecules~\cite{wang2015accurate}.

@@

@@

	\item Alchemlyb: Multipackage free energy analysis
	\url{https://github.com/alchemistry/alchemlyb}~\cite{daviddotson2020alchemistry}.
	\item pymbar: MBAR implementation, but have to roll your own analysis wrapper      
	\url{https://github.com/choderalab/pymbar} \cite{shirts2008statisticallya}.
	\item \href{https://github.com/OpenFreeEnergy/cinnabar}{Cinnabar}: Standardising alchemical free energy analysis. Includes tools for calculating network-wide analyses and deriving absolute free energies using a maximum-likelihood estimator \cite{richard_gowers_2025_15678719}.
        \item \href{https://gitlab.com/RutgersLBSR/fe-toolkit}{FE-Toolkit}: collection of packages for free energy analysis, including network-wide MBAR analysis~\cite{giese2025fe}.
    \item \href{http://www.ties-service.org}{TIES}: Perform statistical analysis of the output of alchemical ensemble simulations and report reliable predictions along with statistical uncertainties for a variety of free energy estimators \url{https://github.com/UCL-CCS/TIES_MD} \cite{bieniek2023}.
	\end{itemize}
\item[] Generally, commercial software will offer more complete pipelines in which standalone analysis applications are not necessarily needed; free and open source packages often require manual analysis but allow more flexibility and modification.
\end{itemize}
